FAT-Pointer based range addresses

### 2024-03-10 papers/ISMM/FlexPointer/paper.tex
added .gitignore entry for binaries
references set

@@

\section{FAT-Pointer based range addresses}

@@

@@

\section{Related work}
Efficient memory management, particularly in the context of 
Translation Lookaside Buffer (TLB) optimization, has been a focal point of 
research and development within computer architecture. Various techniques have been 
proposed to mitigate TLB-related bottlenecks and improve overall system performance.

@@

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

>>>>

% \usepackage[style=authoryear, useprefix = false]{biblatex}

@@

\subsection{Background}

\section{FAT-Pointer based range addresses}
This experiment exploits the FAT pointer to enable faster

@@

\subsection{Fragmentation}

@@

\section{Related work}
Efficient memory management, particularly in the context of 
Translation Lookaside Buffer (TLB) optimization \cite{ad-wood-2003}, has been a focal point of 
research and development within computer architecture. Various techniques have been 
proposed to mitigate TLB-related bottlenecks and improve overall system performance.

@@

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
% \begin{acks}
% To Robert, for the bagels and explaining CMYK and color spaces.
% \end{acks}

\begin{acks}
  To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

% \appendix
